---
title: "SCORE Targets"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 6
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(targets)
library(readr)
library(googledrive)
library(googlesheets4)
library(dplyr)
# Silly workaround to get renv to store these packages
library(hashids)
library(usethis)
library(visNetwork)
tar_unscript()
```

The R package `targets` is a [make](https://www.gnu.org/software/make/)-like tool for reproducibly running the code that generates project products, such as analytic datasets, models, and figures. 

Rendering this file using `rmarkdown::render("targets.Rmd")` executes a series of functions in the correct order to build target files (also known as "targets", e.g., analytic datasets, figures) from source files (e.g., raw data). It also documents the dependencies of the target file, including all files (whether source files or other targets) which are used as inputs to the commands in the functions used to generate the target file.

# Globals

We first define the global options and source functions used to generate target files.

```{targets globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE,
        # Gmail authorization for accessing sheets
        # Set google_oauth_email="youremail@cos.io" in your .Renviron file 
        # to use this document without changing the code.
        gargle_oauth_email = Sys.getenv("google_oauth_email"),
        scipen = 999)

googledrive::drive_auth()
googlesheets4::gs4_auth()

tar_option_set(
  # Packages the targets need to run
  packages = c("BayesFactor",
               "BayesRep",
               "BFF", # Version 4.2.1 REQUIRED
               "dplyr",
               "effectsize",
               "ggExtra",
               "glue",
               "googlesheets4",
               "googledrive",
               "here",
               "kableExtra",
               "lubridate",
               "metaBMA",
               "metafor",
               "osfr",
               "purrr",
               "pwr",
               "readr",
               "ReplicationSuccess",
               "sjPlot",
               "stringr",
               "tibble",
               "tidyr") 
)

# All functions used are found in the folder named "pipeline"
tar_source(files = "pipeline")

```

# Targets

## Raw Data

Most raw data files will have three targets associated with them - one for their ID on OSF, one for the modification date of the file, and one that actually represents the data loaded into R. The modification date targets are set to run every time `tar_make()` is called so that the file is pulled again if it is ever updated online. 

### Journal Metadata

``` {targets raw-journal}
list(
  # journal_metadata_raw.csv ----
  # Metadata about journals that articles were sourced from, including names,
  # ISSNs, and general publication category
  tar_target(journal_metadata_file,
             "tcb8q"),
  tar_target(journal_metadata_moddate,
             get_osf_mod_date(journal_metadata_file),
             cue = tar_cue("always")),
  tar_target(journal_metadata_raw,
             load_osf_csv(journal_metadata_file,
                          journal_metadata_moddate)),
  
  # journal_repro-policies.csv ----
  # Journal policies about reproducibility and data/code sharing
  tar_target(journal_repro_policies_file,
             "24j8s"),
  tar_target(journal_repro_policies_moddate,
             get_osf_mod_date(journal_repro_policies_file),
             cue = tar_cue("always")),
  tar_target(journal_repro_policies,
             load_osf_csv(journal_repro_policies_file,
                          journal_repro_policies_moddate)),
  
  # journal_top-factor.csv ----
  # TOP Factor (2015) standards for journals that articles were sourced from,
  # according to the TOP factor website (https://topfactor.org/journals)
  tar_target(journal_top_factor_file,
             "2bhwe"),
  tar_target(journal_top_factor_moddate,
             get_osf_mod_date(journal_top_factor_file),
             cue = tar_cue("always")),
  tar_target(journal_top_factor,
             load_osf_csv(journal_top_factor_file,
                          journal_top_factor_moddate))
)
```

### Paper-level Metadata

```{targets raw-paper}
list(
  # paper_citations.csv ----
  # Citations in APA format for papers from which claims were extracted
  tar_target(paper_citations_file,
             "wr8a3"),
  tar_target(paper_citations_moddate,
             get_osf_mod_date(paper_citations_file),
             cue = tar_cue("always")),
  tar_target(paper_citations,
             load_osf_csv(paper_citations_file,
                          paper_citations_moddate)),
  
  # paper_metadata_covid.csv ----
  # Metadata for COVID preprints from which claims were extracted
  tar_target(paper_metadata_covid_file,
             "dc3uv"),
  tar_target(paper_metadata_covid_moddate,
             get_osf_mod_date(paper_metadata_covid_file),
             cue = tar_cue("always")),
  tar_target(paper_metadata_covid,
             load_osf_csv(paper_metadata_covid_file,
                          paper_metadata_covid_moddate)),
  
  # paper_metadata_raw.csv ----
  # Raw metadata for papers from which research claims were extracted 
  # (excluding COVID preprints)
  tar_target(paper_metadata_raw_file,
             "j4gkp"),
  tar_target(paper_metadata_raw_moddate,
             get_osf_mod_date(paper_metadata_raw_file),
             cue = tar_cue("always")),
  tar_target(paper_metadata_raw,
             load_osf_csv(paper_metadata_raw_file,
                          paper_metadata_raw_moddate))
)
```

### Original Studies

#### Original Study Claims

```{targets raw-claims}
list(
  # orig_claims_bushel-complex.csv ----
  # Indicates bushel claims where the evidence is anything other than a single
  # statistically significant effect
  tar_target(orig_claims_bushel_complex_file,
             "qjgwb"),
  tar_target(orig_claims_bushel_complex_moddate,
             get_osf_mod_date(orig_claims_bushel_complex_file),
             cue = tar_cue("always")),
  tar_target(orig_claims_bushel_complex,
             load_osf_csv(orig_claims_bushel_complex_file,
                          orig_claims_bushel_complex_moddate)),

  # orig_claims_covid_ta2-ids.csv ----
  # Claims extracted from phase 1 COVID preprints with IDs for human assessment
  # teams. Used to reconcile IDs for process reproducibility work.
  tar_target(orig_claims_covid_ta2_file,
             "q4kca"),
  tar_target(orig_claims_covid_ta2_moddate, 
             get_osf_mod_date(orig_claims_covid_ta2_file),
             cue = tar_cue("always")), 
  tar_target(orig_claims_covid_ta2,
             load_osf_csv(orig_claims_covid_ta2_file,
                          orig_claims_covid_ta2_moddate)),
  
  # orig_claims_p1-covid.csv ----
  # Claims extracted from phase 1 COVID preprints with canonical paper IDs.
  # Preprints were from PsyarXiv, SocArXiv, and medRxiv.
  tar_target(orig_claims_p1_covid_file,
             "94dfs"),
  tar_target(orig_claims_p1_covid_moddate,
             get_osf_mod_date(orig_claims_p1_covid_file),
             cue = tar_cue("always")),
  tar_target(orig_claims_p1_covid,
             load_osf_csv(orig_claims_p1_covid_file,
                          orig_claims_p1_covid_moddate)),
  
  # orig_claims_p1.csv ----
  # Claims extracted from articles during phase 1 (February 2019 to December
  # 2020) with canonical paper IDs
  tar_target(orig_claims_p1_file,
             "na35f"),
  tar_target(orig_claims_p1_moddate,
             get_osf_mod_date(orig_claims_p1_file),
             cue = tar_cue("always")),
  tar_target(orig_claims_p1,
             load_osf_csv(orig_claims_p1_file,
                          orig_claims_p1_moddate)),
  
  # orig_claims_p2-bushel.csv ----
  # Bushel claims from phase 2 with canonical paper IDs. 
  # Rather than focusing on an individual claim in a paper, bushel claim traces 
  # may branch at any point of a paper up until the test description (claim 4)
  tar_target(orig_claims_p2_bushel_file,
             "9m57d"),
  tar_target(orig_claims_p2_bushel_moddate,
             get_osf_mod_date(orig_claims_p2_bushel_file),
             cue = tar_cue("always")),
  tar_target(orig_claims_p2_bushel,
             load_osf_csv(orig_claims_p2_bushel_file,
                          orig_claims_p2_bushel_moddate)),
  
  # orig_claims_p2-single.csv ----
  # Single-trace claims extracted from articles during phase 2 (January 2021 to
  # May 2022) with canonical paper IDs
  tar_target(orig_claims_p2_single_file,
             "nakxy"),
  tar_target(orig_claims_p2_single_moddate,
             get_osf_mod_date(orig_claims_p2_single_file),
             cue = tar_cue("always")),
  tar_target(orig_claims_p2_single,
             load_osf_csv(orig_claims_p2_single_file,
                          orig_claims_p2_single_moddate))
)
```

#### Original Study Variables

```{targets raw-orig-stats}
list(
  # orig_effect-size.csv ----
  # Calculated effect sizes with upper and lower bounds for original studies
  tar_target(orig_effect_size_file,
             "4s3de"),
  tar_target(orig_effect_size_moddate,
             get_osf_mod_date(orig_effect_size_file),
             cue = tar_cue("always")), 
  tar_target(orig_effect_size,
             load_osf_csv(orig_effect_size_file,
                          orig_effect_size_moddate)),
  
  # orig_stats_effective.csv ----
  # Adjusted sample sizes and degrees of freedom for the purpose of 
  # effect size estimation.
  tar_target(orig_stats_effect_file,
             "k5chq"),
  tar_target(orig_stats_effect_moddate,
             get_osf_mod_date(orig_stats_effect_file),
             cue = tar_cue("always")), 
  tar_target(orig_stats_effect,
             load_osf_csv(orig_stats_effect_file,
                          orig_stats_effect_moddate)),
  
  # orig_stats_extended.csv ----
  # Additional statistics for original studies calculated by collaborators at
  # Tilburg University.
  tar_target(orig_stats_extended_file,
             "9fbm8"),
  tar_target(orig_stats_extended_moddate, 
             get_osf_mod_date(orig_stats_extended_file),
             cue = tar_cue("always")), 
  tar_target(orig_stats_extended,
             # Delivered data has everything encased in quotes
             # These are removed before merging into analytic datasets
             load_osf_csv(orig_stats_extended_file,
                          orig_stats_extended_moddate)),
  
  # orig_stats_p1.csv ----
  # Statistics from original articles that underwent replication/reproduction 
  # in phase 1. Each record is a paper that documents the single claim and
  # inferential test selected for that paper. In Phase 1, the (unique)
  # inferential test from the (unique) focal claim is coded and stored across
  # several different workflows, then aggregated into a ground truth version
  # post QA and merging. Original variables may have been coded in either/both
  # of main or repro type pipelines, so there are sometimes multiple rows 
  # per paper.
  tar_target(orig_stats_p1_file,
             "fa6ub"),
  tar_target(orig_stats_p1_moddate,
             get_osf_mod_date(orig_stats_p1_file),
             cue = tar_cue("always")),
  tar_target(orig_stats_p1,
             load_osf_csv(orig_stats_p1_file,
                          orig_stats_p1_moddate)),
  
  # orig_stats_p2_additional.csv ----
  # Statistics from original articles that underwent replications/reproductions
  # in phase 2 that were entered manually later in the process
  tar_target(orig_stats_p2_additional_file,
             "y84gf"),
  tar_target(orig_stats_p2_additional_moddate, 
             get_osf_mod_date(orig_stats_p2_additional_file),
             cue = tar_cue("always")), 
  tar_target(
    orig_stats_p2_additional,
    load_osf_csv(orig_stats_p2_additional_file,
                 orig_stats_p2_additional_moddate,
                 col_types = list(
                   # All entries "F", which should load as char, not logical
                   original_statistic_type_reported = col_character(),
                   original_statistic_analysis_type_statsteam = col_character()
                   )
      )
    ),
  
  # orig_stats_p2_form-outputs.csv ----
  # Statistics from original articles that underwent replications/reproductions
  # in phase 2 that were entered via google form.
  tar_target(orig_stats_p2_form_file,
             "6qg4a"),
  tar_target(orig_stats_p2_form_moddate,
             get_osf_mod_date(orig_stats_p2_form_file),
             cue = tar_cue("always")), 
  tar_target(orig_stats_p2_form,
             load_osf_csv(orig_stats_p2_form_file,
                          orig_stats_p2_form_moddate)),
  
  # orig_stats_p2_manual-entry.csv ----
  # Statistics from original articles that underwent replications in phase 2
  # that were entered manually rather than through the other workflows.
  tar_target(orig_stats_p2_manual_file,
             "dusqm"),
  tar_target(orig_stats_p2_manual_moddate,
             get_osf_mod_date(orig_stats_p2_manual_file),
             cue = tar_cue("always")),
  tar_target(
    orig_stats_p2_manual,
    load_osf_csv(orig_stats_p2_manual_file,
                 orig_stats_p2_manual_moddate,
                 col_types = list(
                   # Empty columns that should load as char, not logical
                   original_statistic_type_reported = col_character(),
                   original_statistic_type_reference = col_character()
                   ))
    ),
  
  # orig_stats_p2_power-outputs.csv ----
  # Statistics from original articles that underwent replications in phase 2
  # that were gathered from power analysis outputs
  tar_target(orig_stats_p2_pwr_file,
             "6cweg"),
  tar_target(orig_stats_p2_pwr_moddate,
             get_osf_mod_date(orig_stats_p2_pwr_file),
             cue = tar_cue("always")),
  tar_target(orig_stats_p2_pwr,
             load_osf_csv(orig_stats_p2_pwr_file,
                          orig_stats_p2_pwr_moddate))
)
```

### Replication Studies

```{targets replications}
list(
  # repli_effective.csv ----
  # Adjusted sample sizes and degrees of freedom for the purpose of 
  # effect size estimation.
  tar_target(repli_effective_file,
             "mhf8d"),
  tar_target(repli_effective_moddate,
             get_osf_mod_date(repli_effective_file),
             cue = tar_cue("always")),
  tar_target(repli_effective,
             load_osf_csv(repli_effective_file,
                          repli_effective_moddate)),

  # repli_effect-size.csv ----
  # Calculated effect sizes with upper and lower bounds for replication studies
  tar_target(repli_effect_size_file,
             "yxw5t"),
  tar_target(repli_effect_size_moddate,
             get_osf_mod_date(repli_effect_size_file),
             cue = tar_cue("always")),
  tar_target(repli_effect_size,
             load_osf_csv(repli_effect_size_file,
                          repli_effect_size_moddate)),
  
  # repli_exclusions.csv ----
  # The replication findings excluded from the main replication reporting 
  # and their exclusion reasons
  tar_target(repli_case_exclusions_file,
             "wq65j"),
  tar_target(repli_case_exclusions_moddate,
             get_osf_mod_date(repli_case_exclusions_file),
             cue = tar_cue("always")), 
  tar_target(repli_case_exclusions,
             load_osf_csv(repli_case_exclusions_file,
                          repli_case_exclusions_moddate)),
  
  # repli_extended.csv ----
  # Additional statistics for replication studies calculated by collaborators 
  # at Tilburg University.
  tar_target(repli_extended_file,
             "e9v5x"),
  tar_target(repli_extended_moddate, 
             get_osf_mod_date(repli_extended_file),
             cue = tar_cue("always")), 
  tar_target(repli_extended,
             load_osf_csv(repli_extended_file,
                          repli_extended_moddate)),
  
  # repli_stats_p1.csv ----
  # Statistics from replication studies in phase 1.
  tar_target(repli_stats_p1_file,
             "cyr63"),
  tar_target(repli_stats_p1_moddate,
             get_osf_mod_date(repli_stats_p1_file),
             cue = tar_cue("always")),
  tar_target(repli_stats_p1,
             load_osf_csv(repli_stats_p1_file,
                          repli_stats_p1_moddate)),
  
  # repli_stats_p2_additional.csv ----
  # Statistics from replication studies in phase 2 that were entered 
  # manually later in the process
  tar_target(repli_stats_p2_additional_file,
             "6jhy7"),
  tar_target(repli_stats_p2_additional_moddate,
             get_osf_mod_date(repli_stats_p2_additional_file),
             cue = tar_cue("always")),
  tar_target(repli_stats_p2_additional,
             load_osf_csv(repli_stats_p2_additional_file,
                          repli_stats_p2_additional_moddate)),
  
  # repli_stats_p2.csv ----
  # Statistics from replication studies in phase 2 that were entered via 
  # google form.
  tar_target(repli_stats_p2_file,
             "7xfpq"),
  tar_target(repli_stats_p2_moddate,
             get_osf_mod_date(repli_stats_p2_file),
             cue = tar_cue("always")),
  tar_target(repli_stats_p2,
             load_osf_csv(repli_stats_p2_file,
                          repli_stats_p2_moddate))
)
```

### Reproduction Studies

```{targets reproductions}
list(
  # repro_prereg-check.csv ----
  # Researcher check-in information for reproduction registrations
  tar_target(repro_prereg_check_file,
             "7kydz"),
  tar_target(repro_prereg_check_moddate,
             get_osf_mod_date(repro_prereg_check_file),
             cue = tar_cue("always")),
  tar_target(repro_prereg_check,
             load_osf_csv(repro_prereg_check_file,
                               repro_prereg_check_moddate)),
  
  # repro_stats_additional.csv ----
  # Statistics from reproduction studies that were entered later in the 
  # process rather than through the google form
  tar_target(repro_stats_additional_file,
             "sw49d"),
  tar_target(repro_stats_additional_moddate,
             get_osf_mod_date(repro_stats_additional_file),
             cue = tar_cue("always")),
  tar_target(repro_stats_additional,
             load_osf_csv(repro_stats_additional_file,
                          repro_stats_additional_moddate)),
  
  # repro_stats.csv ----
  # Statistics from reproduction studies that were entered via google form.
  tar_target(repro_stats_file,
             "h82yc"),
  tar_target(repro_stats_moddate,
             get_osf_mod_date(repro_stats_file),
             cue = tar_cue("always")),
  tar_target(repro_stats,
             load_osf_csv(repro_stats_file,
                          repro_stats_moddate)),
  
  # repro_vor.csv ----
  # Source of the reproduction version of record in cases with multiple
  # reproductions for the same claim
  tar_target(repro_vor_file,
             "k8e7w"),
  tar_target(repro_vor_moddate,
             get_osf_mod_date(repro_vor_file),
             cue = tar_cue("always")),
  tar_target(repro_vor,
             load_osf_csv(repro_vor_file,
                          repro_vor_moddate))
)
```

### Process Reproducibility

```{targets raw-pr}
list(
  # orig-material_author-outreach.csv ----
  # Original study data and code availability based on author outreach efforts
  tar_target(materials_author_outreach_file,
             "uxj48"),
  tar_target(materials_author_outreach_moddate,
             get_osf_mod_date(materials_author_outreach_file),
             cue = tar_cue("always")),
  tar_target(materials_author_outreach,
             load_osf_csv(materials_author_outreach_file,
                          materials_author_outreach_moddate)),
  
  # orig-material_availability.csv ----
  # Original study data and code availability determinations from a 
  # variety of sources
  tar_target(materials_availability_file,
             "dz5cs"),
  tar_target(materials_availability_moddate,
             get_osf_mod_date(materials_availability_file),
             cue = tar_cue("always")),
  tar_target(materials_availability,
             load_osf_csv(materials_availability_file,
                          materials_availability_moddate))
)
```

### Auxiliary Datasets

```{targets aux-data}
list(
  # Non-significant bushels
  # Coding out significant vs non-significant bushel claims
  tar_target(non_significant_bushels_gsheet,
             "1C89wRO_dZ1_qq9Ow0RpaWK2jWteloo9zPS9pW9VdbP0"),
  tar_target(non_significant_bushels_moddate,
             get_google_mod_date(non_significant_bushels_gsheet),
             cue = tar_cue("always")),
  tar_target(non_significant_bushels,
             read_google_sheet(non_significant_bushels_gsheet,
                               non_significant_bushels_moddate,
                               sheet = "claims")),
  
  # RR sourced 
  # All replication and reproduction projects that were matched with a team. 
  tar_target(rr_sourced_gsheet,
             "1EyUGgw8uGaCIP9nLXKh3IwqqU4DoAM4ZV6K5i1dOTHo"),
  tar_target(rr_sourced_moddate,
             get_google_mod_date(rr_sourced_gsheet),
             cue = tar_cue("always")),
  tar_target(rr_sourced,
             read_google_sheet(rr_sourced_gsheet,
                               rr_sourced_moddate,
                               sheet = "sourced",
                               drop_cols = "indicator")),
  
  # Never sourced
  # Reasons why non-matched papers were not plausible for replication
  tar_target(never_sourced_gsheet,
             "1OVfv_dDsfAeBOtx9-IaTNgPJv5-OFaHS4cK45aYsBpo"),
  tar_target(never_sourced_moddate,
             get_google_mod_date(never_sourced_gsheet),
             cue = tar_cue("always")),
  tar_target(never_sourced,
             read_google_sheet(never_sourced_gsheet,
                               never_sourced_moddate,
                               sheet = "never_sourced",
                               drop_cols = c("paper_link", "confidence"))),
  
  # Alternative Power Coding
  tar_target(ser_vs_traditional_gsheet,
             "1hGT5cEnadMVocvu-9LnfnFfZRZadYCjjPiFy41zwxWw"),
  tar_target(ser_vs_traditional_moddate,
             get_google_mod_date(ser_vs_traditional_gsheet),
             cue = tar_cue("always")),
  
  ## Traditional
  tar_target(traditional_power,
             read_google_sheet(ser_vs_traditional_gsheet,
                               ser_vs_traditional_moddate,
                               sheet = "traditional")),
  ## SER
  tar_target(ser_power,
             read_google_sheet(ser_vs_traditional_gsheet,
                               ser_vs_traditional_moddate,
                               sheet = "ser")),
  
  # Preregistration Indicators
  # Whether the original paper mentions preregistration
  tar_target(prereg_indicators_file,
             "1fOO4EoOkM8uswzgFczBlArsHbrf2KFeE"),
  tar_target(prereg_indicators_moddate,
             get_google_mod_date(prereg_indicators_file),
             cue = tar_cue("always")),
  tar_target(prereg_indicators,
             read_google_csv(prereg_indicators_file,
                             prereg_indicators_moddate,
                             col_types = c("clcd"))),
  
  # Summary of methodological approaches in original studies.
  # llm_method_data.csv
  tar_target(llm_method_data_file,
             "vxysn"),
  tar_target(llm_method_data_moddate,
             get_osf_mod_date(llm_method_data_file)),
  tar_target(llm_method_data,
             load_osf_csv(llm_method_data_file,
                          llm_method_data_moddate)),
  
  # Summary of research questions in original studies
  # llm_research_question_table.csv
  tar_target(llm_research_question_table_file,
             "mg794"),
  tar_target(llm_research_question_table_moddate,
             get_osf_mod_date(llm_research_question_table_file)),
  tar_target(llm_research_question_table,
             load_osf_csv(llm_research_question_table_file,
                          llm_research_question_table_moddate)),
  
  # Summary of theoretical frameworks of original studies
  # llm_theory_data.csv
  tar_target(llm_theory_data_file,
             "mp3rq"),
  tar_target(llm_theory_data_moddate,
             get_osf_mod_date(llm_theory_data_file)),
  tar_target(llm_theory_data,
             load_osf_csv(llm_theory_data_file,
                          llm_theory_data_moddate))
)
```

### Correlations Datasets

```{targets correlations}
list(
  # Elicitations ----
  # Elicitations phase 1
  tar_target(melb_p1_osf,
             "7n2qe"),
  tar_target(melb_p1_mod_date, 
             get_osf_mod_date(melb_p1_osf),
             cue = tar_cue("always")), 
  tar_target(melb_p1,
             load_osf_csv(melb_p1_osf,
                          melb_p1_mod_date)),
  
  # Elicitations phase 2
  tar_target(melb_p2_osf,
             "9khpj"),
  tar_target(melb_p2_mod_date, 
             get_osf_mod_date(melb_p2_osf),
             cue = tar_cue("always")), 
  tar_target(melb_p2,
             load_osf_csv(melb_p2_osf,
                          melb_p2_mod_date)),
  
  # Elicitations bushel
  tar_target(melb_bushel_osf,
             "wy9sv"),
  tar_target(melb_bushel_mod_date, 
             get_osf_mod_date(melb_bushel_osf),
             cue = tar_cue("always")), 
  tar_target(melb_bushel,
             load_osf_csv(melb_bushel_osf,
                          melb_bushel_mod_date)),
  
  # Prediction Markets ----
  tar_target(kw_scores_osf,
             "jn9dg"),
  tar_target(kw_scores_mod_date, 
             get_osf_mod_date(kw_scores_osf),
             cue = tar_cue("always")), 
  tar_target(kw_scores,
             load_osf_csv(kw_scores_osf,
                          kw_scores_mod_date)),
  
  # A+ ----
  # A+ sprint 1
  tar_target(ts_s1_osf,
             "56xqd"),
  tar_target(ts_s1_mod_date, 
             get_osf_mod_date(ts_s1_osf),
             cue = tar_cue("always")), 
  tar_target(ts_s1,
             load_osf_csv(ts_s1_osf,
                          ts_s1_mod_date)),
  
  # A+ sprint 2
  tar_target(ts_s2_osf,
             "c28g4"),
  tar_target(ts_s2_mod_date, 
             get_osf_mod_date(ts_s2_osf),
             cue = tar_cue("always")), 
  tar_target(ts_s2,
             load_osf_csv(ts_s2_osf,
                          ts_s2_mod_date)),
  
  # A+ sprint 3
  tar_target(ts_s3_osf,
             "2z96n"),
  tar_target(ts_s3_mod_date, 
             get_osf_mod_date(ts_s3_osf),
             cue = tar_cue("always")), 
  tar_target(ts_s3,
             load_osf_csv(ts_s3_osf,
                          ts_s3_mod_date)),
  
  # A+ bushel
  tar_target(ts_bushel_osf,
             "d8kc3"),
  tar_target(ts_bushel_mod_date, 
             get_osf_mod_date(ts_bushel_osf),
             cue = tar_cue("always")), 
  tar_target(ts_bushel,
             load_osf_csv(ts_bushel_osf,
                          ts_bushel_mod_date)),
  
  # MACROSCORE ----
  # MACROSCORE sprint 1
  tar_target(usc_s1_osf,
             "u8qea"),
  tar_target(usc_s1_mod_date, 
             get_osf_mod_date(usc_s1_osf),
             cue = tar_cue("always")), 
  tar_target(usc_s1,
             load_osf_csv(usc_s1_osf,
                          usc_s1_mod_date)),
  
  # MACROSCORE sprint 2
  tar_target(usc_s2_osf,
             "xc396"),
  tar_target(usc_s2_mod_date, 
             get_osf_mod_date(usc_s2_osf),
             cue = tar_cue("always")), 
  tar_target(usc_s2,
             load_osf_csv(usc_s2_osf,
                          usc_s2_mod_date)),
  
  # MACROSCORE sprint 3
  tar_target(usc_s3_osf,
             "9rcd7"),
  tar_target(usc_s3_mod_date, 
             get_osf_mod_date(usc_s3_osf),
             cue = tar_cue("always")), 
  tar_target(usc_s3,
             load_osf_csv(usc_s3_osf,
                          usc_s3_mod_date)),
  
  # MACROSCORE bushel
  tar_target(usc_bushel_osf,
             "jmdpk"),
  tar_target(usc_bushel_mod_date, 
             get_osf_mod_date(usc_bushel_osf),
             cue = tar_cue("always")), 
  tar_target(usc_bushel,
             load_osf_csv(usc_bushel_osf,
                          usc_bushel_mod_date)),
  
  # Synthetic Markets ----
  # Synthetic markets sprint 1
  tar_target(psu_s1_osf,
             "u7dnr"),
  tar_target(psu_s1_mod_date, 
             get_osf_mod_date(psu_s1_osf),
             cue = tar_cue("always")), 
  tar_target(psu_s1,
             load_osf_csv(psu_s1_osf,
                          psu_s1_mod_date)),
  
  # Synthetic markets sprint 2
  tar_target(psu_s2_osf,
             "efp92"),
  tar_target(psu_s2_mod_date, 
             get_osf_mod_date(psu_s2_osf),
             cue = tar_cue("always")), 
  tar_target(psu_s2,
             load_osf_csv(psu_s2_osf,
                          psu_s2_mod_date)),
  
  # Synthetic markets sprint 3
  tar_target(psu_s3_osf,
             "rc6aw"),
  tar_target(psu_s3_mod_date, 
             get_osf_mod_date(psu_s3_osf),
             cue = tar_cue("always")), 
  tar_target(psu_s3,
             load_osf_csv(psu_s3_osf,
                          psu_s3_mod_date)),
  
  # Sciscore ----
  tar_target(sciscore_file,
             "1YSXZHGfSwEY3zSwReaq6iJQcUT4HT_qE"),
  tar_target(sciscore_moddate,
             get_google_mod_date(sciscore_file),
             cue = tar_cue("always")),
  tar_target(sciscore,
             read_google_csv(sciscore_file,
                             sciscore_moddate)),
  
  # StatCheck ----
  tar_target(statcheck_file,
             "1mcdyTvXchktzYl3IoOLF_pDFLADH2zKi"),
  tar_target(statcheck_moddate,
             get_google_mod_date(statcheck_file),
             cue = tar_cue("always")),
  tar_target(statcheck,
             read_google_tsv(statcheck_file,
                             statcheck_moddate)),
  
  # Robustness ----
  tar_target(m100_file,
             "1EvH6fblQZqMpumlNAj1U6CPH6e68RJMu"),
  tar_target(m100_moddate,
             get_google_mod_date(m100_file),
             cue = tar_cue("always")),
  tar_target(m100,
             read_google_csv(m100_file,
                             m100_moddate)),
  
  # Original claims effect sizes ----
  tar_target(es_file,
             "1k42kApZgmSyyC1A-EsUoimFmNEc5cDuJLZGk4GrQQjA"),
  tar_target(es_moddate,
             get_google_mod_date(es_file),
             cue = tar_cue("always")),
  tar_target(es,
             read_google_sheet(es_file,
                               es_moddate)),
  
  # Original claims significance ----
  # stat_sig and stat_sig_p2 sheets needed, merged
  tar_target(sig_file,
             "1_ZRyWIrPOO3JwzGTUZOMMLo7fKcENAOwW6tmtSxQ_js"),
  tar_target(sig_moddate,
             get_google_mod_date(sig_file),
             cue = tar_cue("always")),
  tar_target(stat_sig,
             read_google_sheet(sig_file,
                               sig_moddate,
                               sheet = "stat_sig")),
  tar_target(stat_sig_p2,
             read_google_sheet(sig_file,
                               sig_moddate,
                               sheet = "stat_sig_p2") %>%
               add_column(p_value_avail = NA_character_)),
  tar_target(sig,
             rbind(stat_sig, stat_sig_p2)),
  
  # Hedging and humility ----
  tar_target(hedge_file,
             "16-7o5x0j2jJEEVw6E1vyUl_2vG2Xnjap"),
  tar_target(hedge_moddate,
             get_google_mod_date(hedge_file),
             cue = tar_cue("always")),
  tar_target(hedge,
             read_google_tsv(hedge_file,
                             hedge_moddate)),
  
  # Original author metadata ----
  tar_target(oa_metadata_file,
             "1YquUUy2-OdUe0DpTR-7qF29f0t5HxOOz"),
  tar_target(oa_metadata_moddate,
             get_google_mod_date(oa_metadata_file),
             cue = tar_cue("always")),
  tar_target(oa_metadata,
             read_google_csv(oa_metadata_file,
                             oa_metadata_moddate)),
  
  # Original author citations ----
  tar_target(oa_citations_file,
             "1gwj6SZfZI8Gw6fcWAsK6f65oKyDsyC-6"),
  tar_target(oa_citations_moddate,
             get_google_mod_date(oa_citations_file),
             cue = tar_cue("always")),
  tar_target(oa_citations,
             read_google_rds(oa_citations_file,
                             oa_citations_moddate) %>%
               # Warnings expected as "NA" the string changes to NA
               mutate(cs = as.numeric(cs),
                      log_count = as.numeric(log_count))),
  
  # DataSeer ----
  tar_target(dataseer_file,
             "1j9680t7HeRV9cRfOlROCNBrH_SAILNe5"),
  tar_target(dataseer_moddate,
             get_google_mod_date(dataseer_file),
             cue = tar_cue("always")),
  tar_target(dataseer,
             read_google_rds(dataseer_file,
                             dataseer_moddate)),
  
  # Automated bibliometric analyses ----
  tar_target(ksu_file,
             "1T1mD0wdCafBm5vu0JaHRl3HuSHVaxEJ2"),
  tar_target(ksu_moddate,
             get_google_mod_date(ksu_file),
             cue = tar_cue("always")),
  tar_target(ksu,
             read_google_csv(ksu_file,
                             ksu_moddate)),
  
  # Extracted open science indicators ----
  tar_target(scholarcy_file,
             "1G1ipJh-aaF5_GdNJU7qUb6Kd2nEWPzyn"),
  tar_target(scholarcy_moddate,
             get_google_mod_date(scholarcy_file),
             cue = tar_cue("always")),
  tar_target(scholarcy,
             read_google_csv(scholarcy_file,
                             scholarcy_moddate))
  
)

```

### Project Management

Some information comes from datasets used in project management.

```{targets rr-projects}
list(
    # status.csv
  # Canonical source for sub-samples of the data
  # Does not contain COVID papers
  tar_target(status_file,
             "1lETiML-WFVGK1MS0ELCZejIaXnDDXYWh"),
  tar_target(status_moddate,
             get_google_mod_date(status_file),
             cue = tar_cue("always")),
  tar_target(status,
             read_google_csv(status_file,
                             status_moddate)),
  # Full Dates
  # Start and end dates of projects
  tar_target(full_dates_file,
             "1YHuWhvE_8tGFPe_L-yYfCYsZ7xBDRxSa"),
  tar_target(full_dates_moddate,
             get_google_mod_date(full_dates_file),
             cue = tar_cue("always")),
  tar_target(full_dates,
             read_google_csv(full_dates_file,
                             full_dates_moddate,
                             col_types = c("cccDDD"))),
  # rr_projects.csv
  tar_target(rr_projects_file,
             "11paXdFzhCmz8ywFomUhZ6qrfp1wlKLIx"),
  tar_target(rr_projects_moddate,
             get_google_mod_date(rr_projects_file),
             cue = tar_cue("always")),
  tar_target(rr_projects_raw,
             read_google_csv(rr_projects_file,
                             rr_projects_moddate)),
  
  # Additional cases - rr projects 
  tar_target(repli_cases_projects,
             read_google_sheet("1y57RNOH96x8dXYc8gxBbCQOmuaMVOoaD0KgJYfoITmg",
                               "2024-11-14T14:03:25.632Z",
                               sheet = "rr_projects")),
  
  # rr_reporting_checkin.tsv
  # This info is used once and then dropped -- REMOVE   
  tar_target(rr_reporting_checkin_file,
             "1jB97FM-desZatqabwBVMPrSYk0qXWFjM"),
  tar_target(rr_reporting_checkin_moddate,
             get_google_mod_date(rr_reporting_checkin_file),
             cue = tar_cue("always")),
  tar_target(rr_reporting_checkin,
             read_google_tsv(rr_reporting_checkin_file,
                             rr_reporting_checkin_moddate)),
  
  # Not Used - REMOVE
  # # p2_repli_vf.csv
  # tar_target(p2_repli_vf_file,
  #            "1fwWX7ebwhBF9IYt2dQyhEByBnRNavOmj"),
  # tar_target(p2_repli_vf_moddate,
  #            get_google_mod_date(p2_repli_vf_file),
  #            cue = tar_cue("always")),
  # tar_target(p2_repli_vf,
  #            read_google_csv(p2_repli_vf_file,
  #                            p2_repli_vf_moddate)),
  
  # rr_attempts_minted.csv
  # Status and tracking for rr projects. 
  # Source for if a replication is a "generalizibility" 
  tar_target(rr_attempts_minted_file,
             "1aHuTwRVeqADWVC4Lxq5n3B4ebbSa9Mqc"),
  tar_target(rr_attempts_minted_moddate,
             get_google_mod_date(rr_attempts_minted_file),
             cue = tar_cue("always")),
  tar_target(rr_attempts_minted_raw,
             read_google_csv(rr_attempts_minted_file,
                             rr_attempts_minted_moddate)),
  
  tar_target(all_rr_attempts_gsheet,
             "13YmuK4UxMEreDNHY4WfjEqDHOi2Htlvwh4wxwbVK25U"),
  tar_target(all_rr_attempts_moddate,
             get_google_mod_date(all_rr_attempts_gsheet),
             cue = tar_cue("always")),
  tar_target(all_rr_attempts,
             read_google_sheet(all_rr_attempts_gsheet,
                               all_rr_attempts_moddate,
                               sheet = "full_sweep")),
  
  ## Raw data with unknown use ----
  # CR_metadata_prepool.csv
  tar_target(CR_metadata_prepool_file,
             "1FnmZMEYiWBhAj0THZvMetdWzuohraPy3"),
  tar_target(CR_metadata_prepool_moddate,
             get_google_mod_date(CR_metadata_prepool_file),
             cue = tar_cue("always")),
  tar_target(CR_metadata_prepool,
             read_google_csv(CR_metadata_prepool_file,
                             CR_metadata_prepool_moddate)),
  
  # p2_id_key.csv
  # Links cannonical paper ID to the IDs used by other teams
  # Does not include COVID papers
  tar_target(p2_id_key_file,
             "1E9af5ncbY2gm7CvHjrWVJt4x_F-ZbyS1"),
  tar_target(p2_id_key_moddate,
             get_google_mod_date(p2_id_key_file),
             cue = tar_cue("always")),
  tar_target(p2_id_key,
             read_google_csv(p2_id_key_file,
                             p2_id_key_moddate))
)
```

## Change Logs

```{targets change-logs}
list(
    # Publications Changelog
  tar_target(pub_changelog_file,
             "1CM0wbYnRvBMIyDVFzvwxw3GVH_uRJ3BXRtdwlxTmS1A"),
  tar_target(pub_changelog_moddate,
             get_google_mod_date(pub_changelog_file),
             cue = tar_cue("always")),
  tar_target(pub_changelog,
             load_changelog(pub_changelog_file,
                            pub_changelog_moddate)),
  
  # orig_input_changelog (Google Sheet)
  tar_target(orig_input_changelog_file,
             "1M8H_76ajxwdhVuuSyIo18BxRrJbMF3hXpAkzYY39g2k"),
  tar_target(orig_input_changelog_moddate,
             get_google_mod_date(orig_input_changelog_file),
             cue = tar_cue("always")),
  tar_target(orig_input_changelog,
             load_changelog(orig_input_changelog_file,
                            orig_input_changelog_moddate)),
  
  # orig_stats_extended_changelog (Google Sheet)
  tar_target(orig_stats_extended_changelog_file,
             "1ODw_EGLJuMqxbce07sagKlEB2klTZXN6XJ92bDSGGy0"),
  tar_target(orig_stats_extended_changelog_moddate,
             get_google_mod_date(orig_stats_extended_changelog_file),
             cue = tar_cue("always")),
  tar_target(orig_stats_extended_changelog,
             load_changelog(orig_stats_extended_changelog_file,
                            orig_stats_extended_changelog_moddate)),
  
  # rr_attempts_minted_changelog (Google Sheet)
  tar_target(rr_attempts_minted_changelog_file,
             "1rlVy9A4jBwQzpxTH4my4FUWaZkq7388YfpRmQOZWihw"),
  tar_target(rr_attempts_minted_changelog_moddate,
             get_google_mod_date(rr_attempts_minted_changelog_file),
             cue = tar_cue("always")),
  tar_target(rr_attempts_minted_changelog,
             load_changelog(rr_attempts_minted_changelog_file,
                            rr_attempts_minted_changelog_moddate)),
  
  # repli_input_changelog (Google Sheet)
  tar_target(repli_input_changelog_file,
             "1jbkVYHLinIN9zXBuPTok26bHjDt69-7D_Z7yVOin3mM"),
  tar_target(repli_input_changelog_moddate,
             get_google_mod_date(repli_input_changelog_file),
             cue = tar_cue("always")),
  tar_target(repli_input_changelog,
             load_changelog(repli_input_changelog_file,
                            repli_input_changelog_moddate)),
  
  # p2_repro_input_changelog (Google Sheet)
  tar_target(p2_repro_input_changelog_file,
             "1c2i_k-RMzTWAC7RD6cqhheToihtS8_C5r5powvRuMDE"),
  tar_target(p2_repro_input_changelog_moddate,
             get_google_mod_date(repli_input_changelog_file),
             cue = tar_cue("always")),
  tar_target(p2_repro_input_changelog,
             load_changelog(p2_repro_input_changelog_file,
                            p2_repro_input_changelog_moddate)),
  
  # repro_supplement_changelog (Google Sheet)
  tar_target(repro_supplement_changelog_file,
             "1OzOpJCJCy5OPYISk1UR5tI0ehNaou-ykAeD7GPZ99ug"),
  tar_target(repro_supplement_changelog_moddate,
             get_google_mod_date(repro_supplement_changelog_file),
             cue = tar_cue("always")),
  tar_target(repro_supplement_changelog,
             load_changelog(repro_supplement_changelog_file,
                            repro_supplement_changelog_moddate)),
  
  tar_target(pr_changelog_gsheet,
             "1zek9Lu-s303ZXs3B84h2vy-sJ1avOZSgpZEsna40pdA"),
  tar_target(pr_changelog_moddate,
             get_google_mod_date(pr_changelog_gsheet),
             cue = tar_cue("always")),
  tar_target(pr_input_changelog,
             load_changelog(pr_changelog_gsheet,
                            pr_changelog_moddate)),
  
  tar_target(oa_changelog_file,
             "1mrH4mPCr6VUrOD8S08hhzD3jdcRjOnMPAF9XfZ0_vH4"),
  tar_target(oa_changelog_moddate,
             get_google_mod_date(oa_changelog_file),
             cue = tar_cue("always")),
  tar_target(oa_changelog,
             load_changelog(oa_changelog_file,
                            oa_changelog_moddate))
)
```

## Intermediate Data

### Publications

```{targets publications}
list(

  # Update and Transform ----
  tar_target(journal_metadata_updated,
             transform_pubs(journal_metadata_raw,
                            pub_changelog))
)
```

### Paper Metadata

```{targets paper-metadata}
list(

  # Transform ----
  # Metadata for covid papers was collected separately from other papers
  # Reconcile differences for merging
  tar_target(covid_metadata,
             transform_covid_metadata(paper_metadata_covid)),
  
  tar_target(non_covid_metadata,
             transform_paper_metadata(paper_metadata_raw, status))
)

```



### Original Study Variables

```{targets original-outcomes}
list(
  ## Merge ----
  tar_target(orig_merged,
             merge_orig_input(orig_stats_p1,
                              orig_stats_p2_pwr,
                              orig_stats_p2_manual,
                              orig_stats_p2_form,
                              orig_claims_p1_covid,
                              orig_stats_p2_additional)),
  ## Update ----
  tar_target(orig_updated,
             update_orig_input(orig_merged,
                               orig_input_changelog)),
  
  tar_target(orig_extended_updated,
             update_orig_extended(orig_stats_extended,
                                  orig_stats_extended_changelog)),
  
  ## Refine ----
  tar_target(orig_dataset,
             export_orig(orig_updated,
                         orig_extended_updated))
)
```

### Replication/Reproduction Projects
```{targets projects}
list(
  ## Merge ----
  tar_target(rr_projects,
             extend_rr_projects(rr_projects_raw,
                                repli_cases_projects)),
  
  ## Update ----
  tar_target(rr_attempts_minted,
             update_attempts_minted(rr_attempts_minted_raw,
                                    rr_attempts_minted_changelog))
)
```



Replications/Reproductions variables data. QC'ed and merged.

```{targets processed-rr}
list(
  # Transform replication form data
  tar_target(replication_qa,
             transform_replication_qa(repli_stats_p2,
                                      rr_attempts_minted)),
  
  tar_target(repli_merged,
             merge_repli_input(repli_stats_p1,
                               replication_qa,
                               rr_reporting_checkin,
                               repli_stats_p2_additional,
                               repli_effective)),
  
  tar_target(repli_export,
             export_repli(repli_merged,
                          repli_input_changelog)),
  
  # Reproduction targets ----
  # Transformed data from forms
  tar_target(repro_data_entry,
             transform_repro_input(repro_stats)),
  
  # Transform reproduction claims
  tar_target(rr_confrontations_repro_claim,
             transform_repro_claims(repro_prereg_check)),
  
  # Merge with additional cases
  tar_target(repro_merged,
             merge_repro(repro_data_entry,
                         repro_stats_additional,
                         repro_vor)),
  
  # Update transformed data from forms
  tar_target(repro_export,
             update_repro(repro_merged,
                          p2_repro_input_changelog)),
  
  # Create repro supplement
  tar_target(repro_supplement_raw,
             transform_repro_outcomes(repro_export,
                                      orig_dataset,
                                      rr_confrontations_repro_claim)),
  
  tar_target(repro_supplement,
             update_repro_supplement(repro_supplement_raw,
                                     repro_supplement_changelog))
)
```

Process reproducibility data. 

```{targets processed-pr}

list(
  
  tar_target(oa_outreach,
             update_oa(materials_author_outreach,
                       oa_changelog)),
  
  tar_target(pr_data_form,
             process_pr_data(materials_availability,
                             orig_claims_covid_ta2,
                             orig_claims_p1_covid)),
           
  tar_target(pr_qc,
             update_pr(pr_data_form,
                       pr_input_changelog))
  
)

```

## Analysis-ready Data

```{targets analytic-data}
list(
  # Information about journals the original studies were from as well as
  # some journal policy information
  tar_target(publications,
             left_join(journal_metadata_updated,
                       journal_top_factor,
                       by = join_by(publication_standard == Journal))),
  
  # Information about individual articles that claims were extracted from
  tar_target(paper_metadata,
             merge_paper_metadata(non_covid_metadata,
                                  covid_metadata,
                                  paper_citations,
                                  publications)),
  
  # Claims made in original studies 
  tar_target(extracted_claims,
             merge_claims(orig_claims_p1,
                          orig_claims_p1_covid,
                          orig_claims_p2_single,
                          orig_claims_p2_bushel,
                          orig_claims_bushel_complex,
                          status,
                          covid_metadata)),
  
  # Original study variables
  tar_target(orig_outcomes,
             create_ov_analytic(orig_dataset,
                                orig_claims_bushel_complex,
                                orig_stats_effect,
                                orig_effect_size,
                                repli_export)),
  
  # Replication study variables
  tar_target(repli_outcomes,
             create_repli_analytic(repli_export,
                                   rr_attempts_minted,
                                   repli_extended,
                                   status,
                                   orig_claims_p2_bushel,
                                   repli_effect_size,
                                   orig_outcomes,
                                   paper_metadata,
                                   repli_case_exclusions)),

  tar_target(repli_binary,
             calculate_repli_binary(repli_outcomes,
                                    orig_outcomes,
                                    paper_metadata)),
  
  # Reproduction study variables
  tar_target(repro_outcomes,
             create_repro_analytic(repro_export,
                                   repro_supplement)),
  
  # Process Reproducibility 
  tar_target(pr_outcomes,
             create_pr_analytic(pr_qc, oa_outreach)),
  
  # Other datasets ----
  tar_target(paper_status_tracking,
             select(status,
                    paper_id,
                    prepool,
                    pool,
                    presample,
                    sample,
                    rejected,
                    RR,
                    p1_delivery,
                    p2_presample,
                    p2_sample,
                    p2_delivery,
                    bushel)),
  
  tar_target(rr_internal_tracking,
             select(all_rr_attempts,
                    rr_id,
                    paper_id,
                    project_guid,
                    field,
                    type,
                    outcome,
                    results_available,
                    registrations,
                    prereg_completion,
                    osf_activity,
                    all_types)),
  
  tar_target(claims_non_significant_bushels,
             select(non_significant_bushels,
                    paper_id,
                    claim4_id,
                    coded_stat_evidence,
                    nonsig)),
  
  tar_target(rr_type_key,
             select(rr_sourced,
                    rr_id,
                    paper_id,
                    type)),
  
  tar_target(repli_all_cases,
             select(repli_export,
                    rr_id,
                    paper_id,
                    rr_type_internal,
                    report_id = unique_report_id,
                    rr_repl_exact_replicated_reference)),

  tar_target(rr_project_dates,
             select(full_dates,
                    rr_id,
                    project_guid,
                    type,
                    started,
                    reg_date,
                    completed)),
  
  tar_target(papers_not_sourced,
             select(never_sourced,
                    paper_id,
                    dr_plausible,
                    dr_reason,
                    dar_plausible,
                    dar_reason)),
  
  tar_target(claims_ser_power,
             select(ser_power,
                    claim_id = unique_claim_id,
                    rr_sample_size_50_for_100 = threshold,
                    rr_sample_size_90_for_75 = s1,
                    rr_sample_size_90_for_50 = s2)),
  
  tar_target(claims_traditional_power,
             select(traditional_power,
                    claim_id,
                    rr_sample_size_50_for_100 = rr_threshold_analytic_sample_size,
                    rr_sample_size_90_for_75 = rr_stage1_analytic_sample_size,
                    rr_sample_size_90_for_50 = rr_stage2_analytic_sample_size)),
  
  tar_target(claims_bushel_ids,
             select(orig_claims_p2_bushel,
                    paper_id,
                    claim4_id)),
  
  # Rename to keep consistent with analysis code
  tar_target(repro_journal_policies,
             journal_repro_policies)
  
)
```

# Run Pipeline

Run the `{targets}` pipeline. Expected warnings:

1) orig_stats_p1: One or more parsing issues
2) replication_qa: There was 1 warning in mutate
3) rr_confrontations_repro_claim: There was 1 warning in mutate.

```{r make}
tar_make()

targets::tar_meta(fields = warnings, complete_only = TRUE)
```

# Output

You can retrieve results from the `_targets/` data store using `tar_read()` or `tar_load()`.

The `targets` dependency graph shows the steps of the pipeline at a high level.

```{r visnetwork}
tar_visnetwork()
```
